Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2022-01-11 latex/ms.tex
add novelty, #14

@@

%Novelty: reproductive potential does not affect for estimating migration number

%Scope of applications
%Case of small migration rate
%Contemporary / historical migration rate

>>>>

There are several novelties of this study. First, we formulated probabilities of kinship pairs randomly chosen between two populations, which provide estimators of the migration number or rate. While similar derivations are found in the context of a mark-recapture method (REF), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled. Our proposed method can avoid such limitations, where such advantages are generally characterized in CKMR method. Second, we reveal that the probabilities and then the estimators are approximately independent of reproductive potential if migration event and the potential are independent. It is useful property of the estimators because heterogeneity of reproductive potential within/between populations are well-known in iteroprous species. Third, we demonstrate applicability that the estimation can be obtained only from the genetic data.

@@

%Novelty: reproductive potential does not affect for estimating migration number, asymmetric migration,

%Scope of applications
%Caveat: selectivity, family correlated migration
%Case of small migration rate
%Contemporary / historical migration rate
